---
title: "My R book"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

# Introduction

In this book, I document some of the common uses of R as a data analysis tool, starting from basics.

Some resources I refer to:

## General
- [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/) - probably the most important of all, for a start
- [Cookbook for R](http://www.cookbook-r.com/)
- [My favorite RStudio tips and tricks](http://datacornering.com/my-favorite-rstudio-tips-and-tricks/)
- [Samuel Chan](https://github.com/onlyphantom)
- [Rcommander guide](https://socialsciences.mcmaster.ca/jfox/Misc/Rcmdr/Getting-Started-with-the-Rcmdr.pdf)
## Linear Algebra
- [Personality Project](https://personality-project.org/r/tutorials/linearalgebra.pdf)
- [R-bloggers](https://www.r-bloggers.com/2019/05/r-companion-to-linear-algebra-step-by-step-part-1/)

## Statistics
- [R-tutor](http://www.r-tutor.com/)
- [SimplyR(College of Staten Island)](https://www.math.csi.cuny.edu/Statistics/R/simpleR/index.html)
- [Statsmethod](https://www.statmethods.net/index.html)

## Data Science
- [R for Data Science](https://r4ds.had.co.nz/index.html)
- [R cookbook](https://rc2e.com/)
- [dplyr cheat sheet](https://4.files.edl.io/b9e2/07/12/19/142839-a23788fb-1d3a-4665-9dc4-33bfd442c296.pdf)
- [TSKam on RPubs](https://rpubs.com/tskam/mosaic_plot)
- [Naimish Agarwal on RPubs](https://rpubs.com/agarwalnaimish/linalgbR)

I have been experiencing compilation errors with Knitr when plots were involved. As such, I will cover visualization in a follow-up.
As there is LaTeX support in R Markdown, I would also consider creating worksheets using RStudio in the future.

> "There is no end to education. It is not that you read a book, pass an examination, and finish with education. The whole of life, from the moment you are born to the moment you die, is a process of learning."
>
> ---Jiddu Krishnamurti


# Basic data structures
## Vectors
Our first data structure is the vector, which is a collection of data of the same class. In R, there are two classes of numerical data (`integer` and `numeric`).

```{r}
# integer
a <- 3:8
a
class(a)
length(a)
```
```{r}
# numeric
b <- c(3.4,5.6,7.8)
class(b)
```
The `character` class stores strings.
```{r}
c <- c("KFC","MacDonald's","Popeyes","Gong Cha")
c[2:3]
```
Notice that c[-3] **drops** the third entry *Popeyes*, unlike in Python where the third entry would be indexed instead.
```{r}
c[-3]
```
We can use logical operators to create boolean masks.
```{r}
a%%3!=0
```
And just like in Python, we can use boolean masks to index vectors.
```{r}
# remove multiples of 3
a[a%%3!=0]
```
```{r}
rep(factor(LETTERS[3:6]), 5)
```
```{r}
# Stock chart look-alike
a <- cumsum(rnorm(1000))+80
# plot(a,type = "l")
# hist(a)
```
Vectors can be used in many ways.

## Data frames
The next data structure is the data frame. Though it has been updated with the tibble, we can still use data frames for many applications.

[Working with tibbles in R](https://www.youtube.com/watch?v=EBk6PnvE1R4)
